Offline Mode for Corporate Mobile Client Security Architecture

### 2017-01-09 docs/papers/2016MONE/2016MONE.tex
correcao do nome do prof. rafael

\author{Tatiana Galibus				\and
        Thiago P. de B. Vieira		\and
        	Edison P. de Freitas			\and
        	Robson O. Albuquerque		\and
        	João Paulo C. L da Costa		\and
        	Rafael T. de Souza Júnior	\and
        Viktor Krasnoproshin			\and
        	Anton Zaleski				\and
        	H.E.R.M. Vissia				\and
        	Giovanni del Galdo
}

\institute{Tatiana Galibus \and Viktor Krasnoproshin \at
              Belarusian State University, Minsk, 4, Nezavisimosti, 220030, Belarus
           \and
           Tatiana Galibus \and Thiago P. B. Vieira \and Robson O. Albuquerque \and João Paulo C. L da Costa \and Rafael T. de Souza Júnior  \at
              University of Brasilia, UnB, FT, ENE, CP: 4386, 70910-900, Brasília, Brazil
           \and
           Edison P. de Freitas \at
				Federal University of Rio Grande do Sul, UFRGS, INF, CP: 15064, 91501-970, Porto Alegre, Brazil
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany
           \and
           Anton Zaleski \and H.E.R.M. Vissia \at
				Byelex Multimedia Products BV Argon 1, 4751 XC Oud Gastel, The Netherlands
}

>>>>

\author{Tatiana Galibus				\and
        Thiago P. de B. Vieira		\and
        	Edison P. de Freitas			\and
        	Robson O. Albuquerque		\and
        	João Paulo C. L da Costa		\and
        	Rafael T. de Sousa Júnior	\and
        Viktor Krasnoproshin			\and
        	Anton Zaleski				\and
        	H.E.R.M. Vissia				\and
        	Giovanni del Galdo
}

\institute{Tatiana Galibus \and Viktor Krasnoproshin \at
              Belarusian State University, Minsk, 4, Nezavisimosti, 220030, Belarus
           \and
           Tatiana Galibus \and Thiago P. B. Vieira \and Robson O. Albuquerque \and João Paulo C. L da Costa \and Rafael T. de Sousa Júnior  \at
              University of Brasilia, UnB, FT, ENE, CP: 4386, 70910-900, Brasília, Brazil
           \and
           Edison P. de Freitas \at
				Federal University of Rio Grande do Sul, UFRGS, INF, CP: 15064, 91501-970, Porto Alegre, Brazil
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany
           \and
           Anton Zaleski \and H.E.R.M. Vissia \at
				Byelex Multimedia Products BV Argon 1, 4751 XC Oud Gastel, The Netherlands
}
